Figure Extra

### 2023-12-15 Figures/Figures_nonTCGA.Rmd
Fix problem NK cells by correcting dictionary

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Vanderbilt <- list()
dict_Vanderbilt[["BPRNACan"]] <- list(`B cells` = c("B"),
                                      CD4 = c("CD4"),
                                      CD8 = c("CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("cancer"),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("M1"),
                                      `M2 macrophages` = c("M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"),
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes, M0 and Neutrophils

@@

dict_Vanderbilt[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(`B cells` = c("B_cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"), # NKT.cells?
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes and NKT.cells

dict_Vanderbilt[["CBSX_LM22"]] <- list(`B cells` = c("B.cells.memory", "B.cells.naive"),
                                      CD4 = c("T.cells.CD4.memory.activated", "T.cells.CD4.memory.resting", "T.cells.CD4.naive"),
                                      CD8 = c("T.cells.CD8", "T.cells.gamma.delta"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophages.M1"),
                                      `M2 macrophages` = c("Macrophages.M2"),
                                      `Mast cells` = c("Mast.cells.activated", "Mast.cells.resting"),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells.activated", "NK.cells.resting"), 
                                      `Plasma cells` = c("Plasma.cells"),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c("T.cells.follicular.helper"),
                                      `T reg. cells` = c("T.cells.regulatory..Tregs.")) # Missing Dendritic.cells.activated, Dendritic.cells.resting, Eosinophils, Macrophages.M0, , Monocytes, Neutrophils

dict_Vanderbilt[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c("Endothelial.cells"),
                                      Cancer = c("Malignant"),
                                      Fibroblasts = c("CAF"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells"), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Macrophages

dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("Malignant.cells"),
                                      Fibroblasts = c("CAFs"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c("Mast.cells"),
                                      `Mural cells` = c(),
                                      NK = c(), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Dendritic.cells Macrophages

dict_Vanderbilt[["Quantiseq"]] <- list(`B cells` = c("B_cell"),
                                      CD4 = c("T_cell_CD4+_(non-regulatory)"),
                                      CD8 = c("T_cell_CD8+"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophage_M1"),
                                      `M2 macrophages` = c("Macrophage_M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK_cell"), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c("T_cell_regulatory_(Tregs)")) # Missing Monocyte Myeloid_dendritic_cell Neutrophil uncharacterized_cell

>>>>

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Vanderbilt <- list()
dict_Vanderbilt[["BPRNACan"]] <- list(`B cells` = c("B"),
                                      CD4 = c("CD4"),
                                      CD8 = c("CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("cancer"),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("M1"),
                                      `M2 macrophages` = c("M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      `NK cells` = c("NK"),
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes, M0 and Neutrophils

@@

dict_Vanderbilt[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(`B cells` = c("B_cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      `NK cells` = c("NK"), # NKT.cells?
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes and NKT.cells

dict_Vanderbilt[["CBSX_LM22"]] <- list(`B cells` = c("B.cells.memory", "B.cells.naive"),
                                      CD4 = c("T.cells.CD4.memory.activated", "T.cells.CD4.memory.resting", "T.cells.CD4.naive"),
                                      CD8 = c("T.cells.CD8", "T.cells.gamma.delta"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophages.M1"),
                                      `M2 macrophages` = c("Macrophages.M2"),
                                      `Mast cells` = c("Mast.cells.activated", "Mast.cells.resting"),
                                      `Mural cells` = c(),
                                      `NK cells` = c("NK.cells.activated", "NK.cells.resting"), 
                                      `Plasma cells` = c("Plasma.cells"),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c("T.cells.follicular.helper"),
                                      `T reg. cells` = c("T.cells.regulatory..Tregs.")) # Missing Dendritic.cells.activated, Dendritic.cells.resting, Eosinophils, Macrophages.M0, , Monocytes, Neutrophils

dict_Vanderbilt[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c("Endothelial.cells"),
                                      Cancer = c("Malignant"),
                                      Fibroblasts = c("CAF"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      `NK cells` = c("NK.cells"), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Macrophages

dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("Malignant.cells"),
                                      Fibroblasts = c("CAFs"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c("Mast.cells"),
                                      `Mural cells` = c(),
                                      `NK cells` = c(), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Dendritic.cells Macrophages

dict_Vanderbilt[["Quantiseq"]] <- list(`B cells` = c("B_cell"),
                                      CD4 = c("T_cell_CD4+_(non-regulatory)"),
                                      CD8 = c("T_cell_CD8+"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophage_M1"),
                                      `M2 macrophages` = c("Macrophage_M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      `NK cells` = c("NK_cell"), 
                                      `Plasma cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c("T_cell_regulatory_(Tregs)")) # Missing Monocyte Myeloid_dendritic_cell Neutrophil uncharacterized_cell
